---
title: 'Calculating the Design Efficiency (A-Efficiency and D-Efficiency)'

output:
  distill::distill_article:
    self_contained: true
    #theme: readable 

---
<p>&nbsp;</p> 

# Calculating the Design Efficiency (A-Efficiency and D-Efficiency)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Description
This application takes the meta-analysis data studying the association between two focal constructs and returns the A-Efficiency and D-Efficiency that captures the extent to which extant studies collectively contributed to our understanding of the focal association.

### Data Input Needed

You can upload your data in the web application below and calculate the A-efficiency and D-efficiency.

The data should have the following characteristics

   - be a `.csv` file
   - have a column specifying the year of the studies ("Year" in the sample data)
   - have a column specifying the correlation of the association being studied ("Corr" in the sample data)
   - all other columns in the data should be the study design factors

***Sample Data***

You can check the desired data structure and also test the functionality of the application using sample data available to download [***here***](data/Efficiency_Best_Next_Studies_Sample_Data_081522.csv){target="_blank"}.

You need to identify the names of the `year` variable, which is "Year" in the sample data, and `correlation` variable,which is "Corr" in the sample data, in your data in the web application below.

For the sample data, the A-Efficiency of the 30 studies examining the correlation between Customer Satisfaction - Retention is 28.13 and the D-Efficiency is 53.15. 

### Web Application

<iframe src="https://bestnextstudy.shinyapps.io/BestNextStudy_Shiny_Eff_Cal/" class="l-screen-inset shaded" height="500px"  width="80%"  frameborder="no" ></iframe>

<p>&nbsp;</p> 

```{r setup_1, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css}
d-title {
    display: none;
  }
```
